\chapter{Summary \& outlook}

The goal of this thesis was to establish a fabrication process to produce \tmdg monolayers of high optical quality by means of encapsulation in \hbng and active control of the charge doping level. This was accomplished by combining the dry transfer technique of ``hot pick-up and stamping'' \cite{pizzocchero_hot_2016, tien_study_2016} with contact lithography and mechanical exfoliation. \textsc{Tmd} monolayers were produced by mechanically exfoliating material from a bulk crystal with adhesive tape. To obtain narrow linewidths they were encasulated in \hbng flakes by picking up \hbng and \tmdg flakes one by one with a \textsc{ppc}-coated \pdms-stamp and dropped in contact with gold electrodes. To verify the function and determine the maximum gate voltage the leaking current through the samples was measured using a lock-in technique.

A combined gate-tunable mono- and bilayer sample of tungsten diselenide was analyzed by means of confocal spectroscopy. Both reflection and photoluminescence spectra were recorded while sweeping the gate voltage to determine intrinsic doping and observe the transition between neutral and negative charge carrier density \cite{wang_probing_2017}.

The observed spectral linewidth of 6--7 meV for the neutral exciton peak is a significant improvement over previous samples, especially because these values can be observed on most of the sample. The intrinsic homogeneous linewidth is expected to be below 2 meV \cite{ajayi_approaching_2017}, so there is still room for improvement.

The good linewidth-related resolution allowed the study of different spectral features while tuning the electron density as well as applying a magnetic field. As a result the transition between a neutral regime and a negatively charged regime could be observed \cite{wang_probing_2017}, in which the neutral exciton peak vanishes along with peaks to the red, that are associated with momentum-indirect excitons. Instead, the trion double feature, that is split by exchange interaction appears 30 meV to the red of the exciton, along with a new set of phonon sidebands, that could be charged counterparts of the peaks in the neutral spectrum. The first phonon sideband, associated with a momentum-indirect exciton with an electron in the $Q$-valley, is energetically close to the trion. Therefore its behavior upon changing the gate voltage was of particular interest. The exchange splitting of 5.2 meV upon the transition to the charged regime as well as a $g$-factor of 11.5 show that this peak is different from the trion. The spectral line associated with the same phonon sideband in the bilayer shows a similar $g$-factor of 12.1, which suggests a relation between both features and is an argument for the phonon sideband model.

The same measurements will also be performed on a sample of tungsten disulfide in the near future.

Other than that, there are also possible advancements in the fabrication process and sample engineering. Uncontrolled thickness of the bottom \hbng flake as well as the 50-90 nm \sio dielectric mean, that in order to create significant electric field strengths, high voltages close to breakdown have to be applied to observe the transition between all relevant regimes. It could be instructive to further extend the gate tunability and there are some viable options to overcome previous limitations. One option is to integrate top and backgate into the heterostructure itself. Using graphene beneath the bottom \hbng flake or above the top, the distance between the gates could be significantly reduced. The result would be a higher field strength close to the sample. The other option would be to retain the substrate as backgate but to discard \sio as as the top layer of the substrate. Using techniques such as atomic layer deposition of materials like aluminum oxide, a thin dielectric can be fabricated \cite{jandhyala_atomic_2012}. A thinner dielectric layer would increase the possible field strength with less complexity of the van-der-Waals heterostructure.

Additionally there are new types of samples that could be fabricated and analyzed. Stacking different \tmdg monolayers on top of each other to form gate-tunable heterobilayers could yield a better understanding of features like second-harmonic generation and layer-indirect excitons. A challenge would be to align the crystal axis of the precursor monolayers, but this could also be an opportunity to study moiré effects in more detail, that originate from a lattice mismatch between the two layers.
Finally, heterostructures as well as single layer samples could be embedded in an optical micro-cavity while also being fully gate tunable. This could help the understanding of exciton-polaritons and phenomena related to cavity physics of \tmds.